AOD Collocated with MAIAC: New Variables

### 2019-08-14 R/non_drake_code_and_md_files/04_AOD_join_MAIAC.Rmd
organize folder
new drake plan

# take each row (sf, df, geometry point) as the argument, create multi-point buffer 
# `aod_buffer` is a multi-buffer:
aod_buffers <- st_buffer(aod_site_km, radius0)
# mapview(aod_buffers) # if you plot this, you will see lots of circles (polygons)
# but of course, after intersect with the base grid, they won't be circles anymore. 
```

@@

# # not sure why mapply doesn't work 
# refDT_sub_list <- mapply(select.refDT.subset, ref_list0 = ref_list[1], point0 = site_list2[1], name0 = name_list[1])

refDT_sub_list <- list()
for (i in 1:length(ref_list)){
  ref_list0 = ref_list[[i]];  point0 = site_list2[[i]]; name0 = name_list[[i]]
  ref_list0$dist <- st_distance(ref_list0, point0)
  ref_list0$Site_Name <- name0
  refDT_sub_list[[i]] <- ref_list0
}
refDT_sub <- rbindlist(refDT_sub_list)
refDT_sub[, dist_km:=as.numeric(dist)/1000] # change distance to km 
refDT_sub <- setDT(refDT_sub)[,.(Site_Name, idLSTpair0, dist_km)]
setnames(refDT_sub, "idLSTpair0", "idLSTpair0_in_buffer")
setkey(refDT_sub, Site_Name)
# save the dataset that links station to all the idLST in the round buffer
# refDT_sub: 3545991 x 3
saveRDS(refDT_sub, "~/Intermediate/AOD_data/190724_refDT_Site_idinBuffer.rds")

@@

# remove some variables 
aod.MODIS.newVars <- function(aod_join_MODIS, MODIS_all){
  aod_join_MODIS <- aod_join_MODIS[!is.na(Optical_Depth_047),]
  aod_join_MODIS[, day:=format(stn_time, "%Y-%m-%d")]
  var_time <- grep("time", names(aod_join_MODIS), value = T)
  aod_join_MODIS <- aod_join_MODIS[, -..var_time]

  setkey(aod_join_MODIS, Site_Name)
  aod_join_buffer <- aod_join_MODIS[refDT_sub, allow.cartesian = T]
  cat("The cartesian joined dataset between collocated Aeronet with MODIS sites data and base grid in each circles, dim is: ", paste(dim(aod_join_buffer),collapse = " x "))

>>>>

# take each row (sf, df, geometry point) as the argument, create multi-point buffer 
# `aod_buffer` is a multi-buffer:
aod_buffers <- st_buffer(aod_site_km, radius0)
# mapview(aod_buffers) # if you plot this, you will see lots of circles (polygons)
# but of course, after intersect with the base grid, they won't be circles anymore.

  site_list <- st_geometry(nemia_aer_m)
  name_list <- as.list(nemia_aer_m$Site_Name) # for recording site names

@@

# # not sure why mapply doesn't work 
refDT_sub_list <- mapply(select.refDT.subset, ref_list, site_list2, name_list)
# # but pmap can work. 
refDT_sub_list <- purrr::pmap(list(ref_list, site_list2, name_list), select.refDT.subset)

# # a loop can work 
for (i in 1:length(ref_list)){
  ref_list0 = ref_list[[i]];  point0 = site_list2[[i]]; name0 = name_list[[i]]
  ref_list0$dist <- sf::st_distance(ref_list0, point0)
  ref_list0$Site_Name <- name0
  refDT_sub_list[[i]] <- ref_list0
}
refDT_sub <- rbindlist(refDT_sub_list)
refDT_sub[, dist_km:=as.numeric(dist)/1000] # change distance to km 
refDT_sub <- setDT(refDT_sub)[,.(Site_Name, idLSTpair0, dist_km)]
setnames(refDT_sub, "idLSTpair0", "nearest_refgrid")
setkey(refDT_sub, Site_Name)
# save the dataset that links station to all the idLST in the round buffer
# refDT_sub: 3545991 x 3
saveRDS(refDT_sub, "~/Intermediate/AOD_data/190724_refDT_Site_idinBuffer.rds")

@@

# aod_join_MODIS is the rolling-joined file, MODIS_all is like lst_terra
aod.MODIS.newVars <- function(aod_join_MODIS, MODIS_all){
  aod_join_MODIS <- aod_join_MODIS[!is.na(Optical_Depth_047),]
  aod_join_MODIS[, day:=format(stn_time, "%Y-%m-%d")]
  var_time <- grep("time", names(aod_join_MODIS), value = T)
  aod_join_MODIS <- aod_join_MODIS[, -..var_time]

  setkey(aod_join_MODIS, Site_Name)
  aod_join_buffer <- aod_join_MODIS[refDT_sub, allow.cartesian = T]
  cat("The cartesian joined dataset between collocated Aeronet with MODIS sites data and base grid in each circles, dim is: ", paste(dim(aod_join_buffer), collapse = " x "))
